%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Valentin Poirot} \\ \vspace{1pt}
%    \small xxx $|$ \href{xxx@xxx}{\underline{xxx@xxx}} $|$ 
   % \href{https://www.linkedin.com/in/valentin-poirot-3077a7197/?lipi=urn%3Ali%3Apage%3Ad_flagship3_feed%3Be8w3COgXRjy%2Bdnw%2FkRi2fA%3D%3D}{\underline{linkedin.com/in/jake}} $|$
 %   \href{https://github.com/valentino-prt}{\underline{github.com/valentino-prt}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Quantitative Developer}{July 2025 -- Present}
      {Société Générale CIB}{Frankfurt, Germany}
      \resumeItemListStart
\resumeItem{Develop \textbf{Python} analytics and trading tools for the \textbf{Global Macro} desk across listed structured products on equities, commodities, FX, rates and crypto.}

\resumeItem{Modernized the desk's trading tools using \textbf{Python}, \textbf{PostgreSQL/TimescaleDB} and \textbf{Grafana} to improve system reliability and support evolving trading requirements.}

\resumeItem{Enhanced daily \textbf{PnL} analysis, trade monitoring tools and real-time \textbf{risk} tracking.}

\resumeItem{Built \textbf{backtesting} tools and historical trading strategy analysis pipelines.}

\resumeItem{Delivered dashboards and automated alerting systems to enable faster trading decisions.}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {DevOps Engineer}{Jan 2025 -- Jun 2025}
      {Société Générale CIB}{Frankfurt, Germany}
      \resumeItemListStart
\resumeItem{Contributed to the stability and performance of \textbf{pre-trade} systems supporting pricing and market-making workflows.}

\resumeItem{Designed and deployed a \textbf{Grafana}-based monitoring stack (metrics, logs, alerts).}
        \resumeItem{Automated operational tasks and service deployment pipelines, enhancing reliability and reducing manual workload.}
    \resumeItemListEnd

    \resumeSubheading
      {Research Engineer (Apprenticeship)}{Sep 2021 -- Sep 2024}
      {CEA Leti}{Grenoble, France}
      \resumeItemListStart
        \resumeItem{Developed and maintained Python-based software for lithography and optical modeling in semiconductor manufacturing workflows}
        \resumeItem{Implemented physical model calibration and simulation pipelines to analyze optical system behavior and improve pre-diction accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IMT Mines Alès}{Alès, France}
      {Engineering Degree in Software Engineering.}{Sep 2021 -- Sep 2024}
    \resumeSubheading
      {Czech Technical University in Prague}{Prague, Czech Republic}
      {University exchange, Computer Science/Statistics.}{Jun 2022 -- Jul 2022}
    \resumeSubheading
      {Toulouse III - Paul Sabatier University}{Toulouse, France}
      {Associate Degree in Electrical and Industrial Computing Engineering.}{Sep 2019 -- Sep 2021}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Semantic Segmentation for Satellite Image Analysis} $|$ \emph{PyTorch, Pandas, NumPy, Matplotlib}}{}
          \resumeItemListStart
            \resumeItem{Implemented GPU-accelerated deep learning models (AlexNet, ResNet, U-Net) using \textbf{CUDA} for large-scale satellite image classification and segmentation (77,000+ samples).}

\resumeItem{Optimized training and inference pipelines for \textbf{performance}, \textbf{memory efficiency} and model accuracy.}

\resumeItem{Built an interactive UI for visualization of model outputs and dataset exploration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Design and Optimization of a Cloud-based Social Network} $|$ \emph{AWS, Python, Celery, Redis}}{}
          \resumeItemListStart
            \resumeItem{Designed and deployed a cloud-native social network on \textbf{AWS} using microservices and scalable architecture.}

\resumeItem{Implemented asynchronous task processing using \textbf{Celery} and \textbf{Redis}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{

\textbf{Languages}{: Python, C++, SQL (PostgreSQL)} \\

\textbf{Frameworks \& Libraries}{: Pandas, NumPy, Polars, PyTorch, FastAPI, Matplotlib} \\

\textbf{Technologies}{: Linux, Git, Docker, TimescaleDB, Grafana, Prometheus, AWS}
}}
\end{itemize}


%-----------HOBBIES-----------
\section{Hobbies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Trail Running \& Alpinism}{: Passion for outdoor challenges and endurance sports.} \\
      \textbf{Cooking}{: Enjoy experimenting with new recipes.} }}
 \end{itemize}


%-------------------------------------------
\end{document}
